---
title: "code"
output: html_document
---
# Notes

- Check if json import is handled correctly in load.data function
- Implement language filtering for data retrieval


# Generic functions:
```{r}
##################################################################################
## loading/installing packages
##################################################################################
load.package = function(package.name){
  package.name = as.character(substitute(package.name))
  if(require(package.name, character.only = TRUE)) { 
    message(paste(package.name, ' loaded', sep = ""))
  } else {
    install.packages(package.name)
  }
}

##################################################################################
## Load data from web or from disk if already stored
##################################################################################

load.data = function(url, type = "xml", file.name, overwrite = FALSE){
  load.package(RCurl)
  
  if(file.exists(file.name) & overwrite == FALSE){
    # print(1)
    return(readRDS(file.name))
  } else {
    # print(2)
    var = switch(type,                     #add additional data sources here
                 xml  = xmlParse(url),
                 json = getURL(url))       #check if correct! Pass apa.api urls?
    saveRDS(var, file = file.name)
    return(var)
  }
}

##################################################################################
## Convert UNIX time stamp to date object and vice versa
##################################################################################

unix2date = function(time.stamp){
  val = time.stamp
  as.POSIXct(val, origin="1970-01-01")
  as.Date(as.POSIXct(val, origin="1970-01-01"))
}

date2unix = function(year, month, day){
  #returns UNIX time: seconds since 01.01.1970 GMT
  as.double(as.POSIXct(as.Date(paste(year, month, day, sep="-")))) 
}

##################################################################################
## Build APA query
##################################################################################
# For example see: http://api.ots.at/wizard/ and
# http://api.ots.at/doku/  for more details

apa.query = function(AppID, channel="", content="alle", 
                     from = 1422745200, to = 1422745200, 
                     number = 10, format = "json"){ 

apa.url = paste("http://www.ots.at/api/liste?app=", AppID,
                "&query=","",   
                "&channel=", channel,         # Finanzen, ...
                "&inhalt=", content,          # filter for pdfs, images, ...
                "&von=", from,                # unix time stamp
                "&bis=", to,                  # unix time stamp
                "&anz=", number,              # mind. , standard , max.
                "&felder=", "",               # CHECK if that works! use %20 as space? see: http://api.ots.at/doku/
                "&format=", format,           # json, rss
                sep = "")

return(apa.url)
}
```

# Data retrieval:

http://api.ots.at/ (api allows specification of fields to be downloaded)

APA finance free trial?:
http://www.apa.at/Site/APA_PB_Finance_FinanceFeed.pdf

Other possible sources:

- WISO
- DGAP: http://www.dgap.de/dgap/DGAP/Twitter/
- https://www.brn-ag.de/person/1688/1 (summary of adhoc news, daily)
- http://www.boerseradio.at/firma/346
- http://library.pressdisplay.com/pressdisplay/de/viewer.aspx
- RSS adhoc: http://www.rss-verzeichnis.de/nachrichten/ausland/1872-finanztreff-adhoc
- http://wienerboerse.archiv.apa.at/ans/WBAG/liste.htm?lang=LANG_DE
- http://webnews.pressetext.com/xml (XML & RSS for AUT, CH, DE)
- http://www.ots.at/rss (Economy and adhoc!)

Use economy news, unemployment, adhoc together?

## RSS
```{r}
load.package(XML)

xml.url = "http://www.ots.at/rss/finanzen/"

rss_test = load.data(xml.url, type = "xml", file.name = "rss_test")

dataframe.rss = xmlToDataFrame(rss_test)
```

## JSON
```{r}
# load.package(RJSONIO)
# 
# isValidJSON("apa.json")
# apa.test = fromJSON(content = "apa.json")

load.package(jsonlite)
apa.test = fromJSON("apa.json")
apa.test.content = apa.test$ergebnis
# class(apa.test.content) #jsonlite should be able to convert JSON to dataframe
apa.test.meta = apa.test$meta
```

## Twitter
```{r}

```


# Data transformation:

- SnowballC
- ...

```{r}

```

# Inspecting the text data:
Wordclouds etc?

# Analysis

- RTextTools  

```{r}

```


