---
title: "code"
output: html_document
---
# Notes

- Check if json import is handled correctly in load.data function
- Implement language filtering for data retrieval

by next week:
- write function to generate API url for presseportal (Christoph - done)
  - language option (EN/DE)
  - option to load xml or json
  - number of entries or time horizon
- consolidate all functions to 1.read data 2.write to dataframe/corpus (Ashish)
- create a package out of this (?)


# Generic functions:
```{r}
##################################################################################
## loading/installing packages
##################################################################################
load.package = function(package.name){
  package.name = as.character(substitute(package.name))
  if(require(package.name, character.only = TRUE)) { 
    message(paste(package.name, ' loaded', sep = ""))
  } else {
    install.packages(package.name)
  }
}

##################################################################################
## Load data from web or from disk if already stored
##################################################################################

load.data = function(url, format = "xml", file.name, overwrite = FALSE){
  load.package(RCurl)
  
  if(file.exists(file.name) & overwrite == FALSE){
    # print(1)
    return(readRDS(file.name))
  } else {
    # print(2)
    var = switch(format,                     #add additional data sources here
                 xml  = xmlParse(url),
                 json = getURL(url))       #check if correct! Pass apa.api urls?
    saveRDS(var, file = file.name)
    return(var)
  }
}

##################################################################################
## Convert UNIX time stamp to date object and vice versa
##################################################################################

unix2date = function(time.stamp){
  val = time.stamp
  as.POSIXct(val, origin="1970-01-01")
  as.Date(as.POSIXct(val, origin="1970-01-01"))
}

date2unix = function(ddmmyyyy.vec){
  year  = ddmmyyyy.vec[3]
  month = ddmmyyyy.vec[2]
  day   = ddmmyyyy.vec[1]
  #returns UNIX time: seconds since 01.01.1970 GMT
  as.double(as.POSIXct(as.Date(paste(year, month, day, sep="-")))) 
}

##################################################################################
## Build APA/DPP query
##################################################################################
# For example see: http://api.ots.at/wizard/ and
# http://api.ots.at/doku/  for more details

apa.query = function(AppID, lang = "en", channel="", content="alle", 
                     date.from = c(01,01,2015), date.to = c(10,02,2015), 
                     number = 10, format = "json"){ 
  
  from = date2unix(date.from)
  to   = date2unix(date.to)
 
language = switch(lang,                    
            en  = "%28slugline%3D%22euro+adhoc%22+and+%28end+of+announcement%29%29",
            de  = "%28%22euro+adhoc%22+and+%28Ende+der+Mitteilung%29%29")
  
  apa.url = paste("http://www.ots.at/api/liste?app=", AppID,
                "&query=", language,           # en/de
                "&channel=", channel,         # Finanzen, ...
                "&inhalt=", content,          # filter for pdfs, images, ...
                "&von=", from,                # unix time stamp
                "&bis=", to,                  # unix time stamp
                "&anz=", number,              # mind. , standard , max.
                "&format=", format,           # json, rss
                sep = "")

return(apa.url)
}

dpp.query = function(AppID, limit = 50, start = 0, 
                     format = "json", lang = "en", teaser = 1){
                     
  
  dpp.url = paste("http://api.presseportal.de/api/ir/adhoc?api_key=", AppID,
                  "&limt=", limit,          # 0-50
                  "&start=", start,         # how many articles after latest
                  "&format=", format,       # json, xml
                  "&lang=", lang,           # en, de
                  "&teaser=", teaser,       # teaser = 0/1
                  sep = "")
                  
return(dpp.url)
}

##################################################################################
## Run query
##################################################################################
# 1. generate url from APA/DPP
apa.url = apa.query("327be26c9e0ef236d9576720647c4d92", format = "json")
dpp.url = dpp.query("e79c7f82be0b69ec33710a6f5b1651f2", format = "json")

# 2. pass url to load.data
apa.data = load.data(url = apa.url, format = "json", 
                     file.name = "apa.test", overwrite = F)
dpp.data = load.data(url = dpp.url, format = "json", 
                     file.name = "dpp.test", overwrite = F)

# 3. write to dataframe
load.package(jsonlite)

# apa.dataframe =  fromJSON(print(quote=F, apa.data))
# dpp.dataframe =  fromJSON(print(quote=F, dpp.data))
```
apa api: 327be26c9e0ef236d9576720647c4d92
dpp api: e79c7f82be0b69ec33710a6f5b1651f2

# Data retrieval example links:
http://api.presseportal.de/api/ir/adhoc?api_key=e79c7f82be0b69ec33710a6f5b1651f2&limt=20&start=0&format=json&lang=en&teaser=1

http://www.ots.at/api/liste?app=327be26c9e0ef236d9576720647c4d92&query=%28slugline%3D%22euro+adhoc%22+and+%28end+of+announcement%29%29&channel=finanzen&inhalt=alle&von=1424991600&bis=1425164399&anz=10&format=json

## RSS
```{r}
load.package(XML)

xml.url = "http://www.ots.at/rss/finanzen/"

rss_test = load.data(xml.url, type = "xml", file.name = "rss_test")

dataframe.rss = xmlToDataFrame(rss_test)
```

## JSON
```{r}
# load.package(RJSONIO)
# 
# isValidJSON("apa.json")
# apa.test = fromJSON(content = "apa.json")

load.package(jsonlite)
apa.test = fromJSON("apa.json")
apa.test.content = apa.test$ergebnis
# class(apa.test.content) #jsonlite should be able to convert JSON to dataframe
# will be done in future
apa.test.meta = apa.test$meta
```

## Twitter
```{r}

```


# Data transformation:

- SnowballC
- ...

```{r}

```

# Inspecting the text data:
Wordclouds etc?

# Analysis

- RTextTools  

```{r}

```


